Feasibility Study for the Final State $hh\rightarrow (b\bar{b})(b\bar{b})$

### 2015-01-22 doc/HH4b_Documentation.tex
added s/b to b-tagging exercise

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Process & $\sigma_{\mathrm{tot}}$ & After b-tag & \% selected & \% Naive selection \\
\hline \hline
$H\bar{H}$ & $1.729 \times 10^{-2}$ pb & $1.565\times 10^{-3}$ pb & \textbf{9.050\%} & 40.96\% \\
\hline
$b\bar{b}b\bar{b}$ & $1.016 \times10^3$ pb & $93.46$ pb & \textbf{9.199\%} & 40.96\%\\
$b\bar{b}jj$ &  $4.076 \times 10^5$ pb & 103.904 pb & \textbf{0.026\%} & 0.0064\% \\
\hline
\end{tabular}
\end{center}
\caption{$b$-tagging analysis performed upon the samples described in Section~\ref{sec:samples}. Cross-sections are given for the samples before and after the application of the b-tagging procedure whereby the four hardest jets in the event are used, and the flat selection efficiency and mis-tag rates applied. The percentage of cross-section surviving the selection is shown, along with the naive expectation ($\epsilon_b^{n_b}\epsilon_l^{n_l}$) for comparison.} \label{tab:btageff1}
\end{table}%

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
Process & $\sigma_{\mathrm{tot}}$ (4 Jets $p_T>40$ GeV) & After b-tag & \% selected  \\
\hline \hline
$H\bar{H}$ & $1.081 \times 10^{-2}$ pb & $8.1147\times 10^{-4}$ pb & 7.467\% \\
\hline
$b\bar{b}b\bar{b}$ & $7.239 \times10^1$ pb & $3.961$ pb & 5.472\% \\
$b\bar{b}jj$ &  $2.137 \times 10^4$ pb & 4.779 pb & 0.0224\% \\
\hline
\end{tabular}
\end{center}
\caption{Summary of the $b$-tagging procedure of the UCL analysis. Presented as in Table~\ref{tab:btageff1}. In this case the total cross-sections are presented after a cut requiring four anti-$k_T$ R=0.5 jets with $p_T>40$ GeV in the final state. The percentage selected column is given for the $b$-tagging stage \emph{only} for comparison.}\label{tab:UCLbtag}
\end{table}%

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Process & $\sigma_{\mathrm{tot}}$ & After b-tag & \% selected & \% Naive selection \\
\hline \hline
$H\bar{H}$ & $1.729 \times 10^{-2}$ pb & $1.565\times 10^{-3}$ pb & \textbf{9.050\%} & 40.96\% \\
\hline
$b\bar{b}b\bar{b}$ & $1.016 \times10^3$ pb & $93.46$ pb & \textbf{9.199\%} & 40.96\%\\
$b\bar{b}jj$ &  $4.076 \times 10^5$ pb & 103.904 pb & \textbf{0.026\%} & 0.0064\% \\
\hline
\textbf{S/B} & $4.23 \times 10^{-8}$ & $7.93 \times 10^{-6}$& \multicolumn{2}{c}{}\\
\cline{1-3}
\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $4.68 \times 10^{-2}$ & $1.93 \times 10^{-1}$& \multicolumn{2}{c}{}\\
\cline{1-3}
\end{tabular}
\end{center}
\caption{$b$-tagging analysis performed upon the samples described in Section~\ref{sec:samples}. Cross-sections are given for the samples before and after the application of the b-tagging procedure whereby the four hardest jets in the event are used, and the flat selection efficiency and mis-tag rates applied. The percentage of cross-section surviving the selection is shown, along with the naive expectation ($\epsilon_b^{n_b}\epsilon_l^{n_l}$) for comparison. Finally, the signal-to-background ratio and significance are given both before and after the b-tagging, for $\mathcal{L}=$ 3 ab$^{-1}$.} \label{tab:btageff1}
\end{table}%

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
Process & $\sigma_{\mathrm{tot}}$ (4 Jets $p_T>40$ GeV) & After b-tag & \% selected  \\
\hline \hline
$H\bar{H}$ & $1.081 \times 10^{-2}$ pb & $8.1147\times 10^{-4}$ pb & 7.467\% \\
\hline
$b\bar{b}b\bar{b}$ & $7.239 \times10^1$ pb & $3.961$ pb & 5.472\% \\
$b\bar{b}jj$ &  $2.137 \times 10^4$ pb & 4.779 pb & 0.0224\% \\
\hline
\textbf{S/B} & $5.04 \times 10^{-7}$ & $9.28 \times 10^{-5}$& \multicolumn{1}{c}{}\\
\cline{1-3}
\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $1.27 \times 10^{-1}$ & $4.75 \times 10^{-1}$& \multicolumn{1}{c}{}\\
\cline{1-3}
\end{tabular}
\end{center}
\caption{Summary of the $b$-tagging procedure of the UCL analysis. Presented as in Table~\ref{tab:btageff1}. In this case the total cross-sections are presented after a cut requiring four anti-$k_T$ R=0.5 jets with $p_T>40$ GeV in the final state. The percentage selected column is given for the $b$-tagging stage \emph{only} for comparison.}\label{tab:UCLbtag}
\end{table}%
